QPLIB: A Library of Quadratic Programming Instances

### 2018-08-24 QPLIB-3.tex
remove todo

We now report some graphs that help in illustrating the main features
of the instances. In Figure~\ref{fig:distribution}~(left) we plot the number
of variables (horizontal axis) versus the number of constraints
(vertical axis), both in logarithmic scale. Continuous instances are
marked with ``$+$'' and discrete ones with ``$\times$''.
\textcolor{green}{Box constraints are not counted as constraints.} \todo{Ambros: From text, tables, and Figure~1 did I correctly infer that variable bounds are not counted as constraints?  The 23 ``none'' in the discrete table seem to be the blue crosses on the x-axis, but then where do the 3 red ``+'' on the x-axis come from?  Are these continuous instances with box constraints and some boxes are infinite?  Should there be a ``none'' in the continuous table?}
The figure shows
that the library contains a quite diverse set of instances in
terms of number of variables and constraints. {The record on the maximal number of variables and constraints (both $\approx 1,000,000$) is set by the instances QPLIB\_8547 and QPLIB\_9008.}
Figure~\ref{fig:distribution}~(right) plots the number of nonzero elements in the gradient of the objective function and the Jacobian and the number of these nonzeros corresponding to nonlinear variables, that is, it counts the appearances of variables in objectives and constraints and how often such an appearance is in a quadratic term.

>>>>

We now report some graphs that help in illustrating the main features
of the instances. In Figure~\ref{fig:distribution}~(left) we plot the number
of variables (horizontal axis) versus the number of constraints
(vertical axis), both in logarithmic scale. Continuous instances are
marked with ``$+$'' and discrete ones with ``$\times$''.
\textcolor{green}{Box constraints are not counted as constraints.}
The figure shows
that the library contains a quite diverse set of instances in
terms of number of variables and constraints. {The record on the maximal number of variables and constraints (both $\approx 1,000,000$) is set by the instances QPLIB\_8547 and QPLIB\_9008.}
Figure~\ref{fig:distribution}~(right) plots the number of nonzero elements in the gradient of the objective function and the Jacobian and the number of these nonzeros corresponding to nonlinear variables, that is, it counts the appearances of variables in objectives and constraints and how often such an appearance is in a quadratic term.
